`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-11-13 paper/paper.qmd
Shorten paper

The six covariates are:

- $|i-j|$, 
- $|i-j|^{2}$, 
- $i + j$, 
- $i \times j$, 
- $\text{max}(i, j)$ and 
- $\text{min}(i, j)$.

These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix). The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting. The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children. The spline-transformed $\text{max}(i, j)$ and $\text{min}(i, j)$ terms give the higher rates of at-home contact among younger people of similar ages and with their parents.

```{r}
#| label: partial-plots-create
#| echo: false

@@

Some future directions for this software include:

* integrating model fitting methods with contact survey prepared using the `socialmixr` R package [@socialmixr];
* enabling prediction to arbitrary age brackets, e.g. monthly age bins for infants;
* fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix;
* providing estimates of uncertainty in contact matrices;
* adding methods to include household size distributions in predictions of contacts in the 'home' setting;

>>>>

The covariate capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix). The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting. 
```{r}
#| label: partial-plots-create
#| echo: false

@@
